### 2024-11-15 conteudo/apendices/gray.tex
fix typo
change to related tools for some parts

\chapter{Gray Literature tools explored}

@@

This appendix contains the the list of gray literature tools 
explored in this initial exploratory research mentioned
in the Introduction. To test this tools, we created a simple 
toy codebase with multiples duplicated code in C.

@@

Tools with paywalls do not meet our requirements, so this 
tool was initially skipped. Out of curiosity, we tried it 
ourselves, and it did not work correctly with our toy
dataset of code duplications.

>>>>

\chapter{Related tools explored}

@@

This appendix contains the the list of related tools 
explored in this initial exploratory research mentioned
in the Introduction. To test this tools, we created a simple 
toy codebase with multiples duplicated code in C.

@@

Tools with paywalls do not meet our requirements, so this 
tool was initially skipped. Out of curiosity, we tried it 
ourselves, and it did not work correctly with our toy
codebase of code duplications.

### 2024-11-15 conteudo/eval/eval.tex
change to related tools for some parts

To finalize this report, we present the current state of our research. As of the 
time of writing, we have finished \textbf{Phase I} of this research, 
which includes the implementation of 
the proposed tool and the evaluation of the tool through both formal literature 
and empirical analyses. This chapter begins with the presentation of the results 
from the tool evaluation. Next, we present a preliminary experiment we are currently 
conducting to assess the viability of our Ethnographic Study. Finally, we outline 
the next steps in this research.

>>>>

To finalize this report, we present the current state of our research. As of the 
time of writing, we have finished \textbf{Phase I} of this research, 
which includes the implementation of 
the proposed tool and the evaluation of the tool through both a method from the 
literature and an empirical analyses. This chapter begins with the presentation of 
the results from the tool evaluation. Next, we present a preliminary experiment 
we are currently conducting to assess the viability of our Ethnographic Study. 
Finally, we outline the next steps in this research.

### 2024-11-15 conteudo/introduction/intro.tex
change to related tools for some parts

Given the unsuccessful results of our search in the formal literature, we
turned to gray literature for solutions but were also met with limited success.
The best solutions we found in the gray literature were primitive, merely
identifying every pair of code files that are duplications. The code files in
the AMD Display driver containing duplicated code typically have specific code
unique to each file. Therefore, a solution that identifies duplication in a
deeper context is necessary to find accurate duplications within the Linux
kernel context. 
The list of gray literature tools examined in this exploratory research 
is available in Appendix A \ref{app:gray}.

>>>>

Given the unsuccessful results of our search in the formal literature, we
turned to explore related tools not present in literature for solutions, but were also met 
with limited success.
The best solutions we found were primitive, merely
identifying every pair of code files that are duplications. The code files in
the AMD Display driver containing duplicated code typically have specific code
unique to each file. Therefore, a solution that identifies duplication in a
deeper context is necessary to find accurate duplications within the Linux
kernel context. 
The list of related tools examined in this exploratory research 
is available in Appendix \ref{app:gray}.
